Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-22 docs/papers/roofline_model/gocean_roofline.tex
roofline: add beginnings of discussion of roofline results

\begin{figure}
\centering
\includegraphics[width=120mm]{roofline_archer}
\caption{Comparison of the performance achieved by nemolite2d and
  Shallow on the E5-2697}
\label{FIG_roofline_archer}
\end{figure}

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=120mm]{roofline_archer}
\caption{Comparison of the performance achieved by NEMOLite2D and
  Shallow on the E5-2697 CPU.}
\label{FIG_roofline_archer}
\end{figure}

@@

In Figure~\ref{FIG_roofline_haswell} we plot the Roofline model
obtained for the E5-1620 CPU. In order to investigate the poor
performance of the u-Momentum kernel of NEMOLite2D, we also show the
performance of the (simpler) Continuity kernel from that code. As we
would expect, the performance of the u-Momentum kernel remains poor on
this CPU. However, the Continuity kernel performs well. The
working-set sizes for this kernel for the $128^2$ and $256^2$ domains
are approximately 1~MB and 4.2~MB, respectively. Both of these should
therefore fit comfortably in L3 cache. However, again, this kernel is
one of several within the time-stepping loop of NEMOLite2D. For the
$128^2$ domain this loop as a whole has a working-set size of
$18\times128^2\times 8$ bytes or 2.4~MB. {\bf Again, this should all
  fit comfortably in l3 cache so why are we nowhere near the L3
  bandwidth limit?}
